Spotify Data

### 2024-11-21 paper/paper.qmd
Added Transparency to Graphs

The dataset used in this analysis is the songs of David Tao sourced from Spotify (@spotify). It records various aspects of the songs by David from 1997 to present.

@@

data |>
  ggplot(aes(x = tempo, y = valence)) +
  geom_point(col = "lightblue") +
  geom_smooth() +
  labs(x = "Tempo", y = "Valence")
```

@@

data |>
  ggplot(aes(x = album_release_date, y = energy)) +
  geom_point(col = "lightblue") +
  geom_smooth() +
  labs(x = "Date Released", y = "Energy")
```

@@

summarise_energy <- data |>
  summarise(Mean = round(mean(energy), 3),
            Median = round(median(energy), 3),
            Variance = round(var(energy), 3),
            Min = round(min(energy), 3),
            Max = round(max(energy), 3),
            IQR = round(IQR(energy), 3)
  )
kable(summarise_energy, format = "markdown")
```

@@

summarise_valence <- data |>
  summarise(Mean = round(mean(valence), 3),
            Median = round(median(valence), 3),
            Variance = round(var(valence), 3),
            Min = round(min(valence), 3),
            Max = round(max(valence), 3),
            IQR = round(IQR(valence), 3)
  )
kable(summarise_valence, format = "markdown")
```

@@

summarise_tempo <- data |>
  summarise(Mean = round(mean(tempo), 3),
            Median = round(median(tempo), 3),
            Variance = round(var(tempo), 3),
            Min = round(min(tempo), 3),
            Max = round(max(tempo), 3),
            IQR = round(IQR(tempo), 3)
  )
kable(summarise_tempo, format = "markdown")
```

>>>>

The dataset used in this analysis is about the songs of David Tao, sourced from Spotify (@spotify). It was accessed by an API. It records various aspects of the songs by David from 1997 to present.

@@

data |>
  ggplot(aes(x = tempo, y = valence)) +
  geom_point(col = "lightblue", alpha = 0.8) +
  geom_smooth() +
  labs(x = "Tempo", y = "Valence")
```

@@

data |>
  ggplot(aes(x = album_release_date, y = energy)) +
  geom_point(col = "lightblue", alpha = 0.8) +
  geom_smooth() +
  labs(x = "Date Released", y = "Energy")
```

@@

summarise_energy <- data |>
  summarise(Mean = round(mean(energy), 1),
            Median = round(median(energy), 1),
            Variance = round(var(energy), 1),
            Min = round(min(energy), 1),
            Max = round(max(energy), 1),
            IQR = round(IQR(energy), 1)
  )
kable(summarise_energy, format = "markdown")
```

@@

summarise_valence <- data |>
  summarise(Mean = round(mean(valence), 1),
            Median = round(median(valence), 1),
            Variance = round(var(valence), 1),
            Min = round(min(valence), 1),
            Max = round(max(valence), 1),
            IQR = round(IQR(valence), 1)
  )
kable(summarise_valence, format = "markdown")
```

@@

summarise_tempo <- data |>
  summarise(Mean = round(mean(tempo), 1),
            Median = round(median(tempo), 1),
            Variance = round(var(tempo), 1),
            Min = round(min(tempo), 1),
            Max = round(max(tempo), 1),
            IQR = round(IQR(tempo), 1)
  )
kable(summarise_tempo, format = "markdown")
```
